Claret: Using Data Types for Highly Concurrent Distributed Transactions

### 2015-02-14 rmd/paper.Rmd
incorporate latest plots: update throughput & add stress throughput

abstract: |
  Building database applications out of data structures rather than simple string values allows the flexibility and fine-grained control of typical key-value databases while providing better performance and scalability. Composing transactions out of linearizable data structure operations exposes concurrency in a safe way, making it simple to implement efficiently and easy to reason about.
---
```{r setup, include=FALSE}
opts_chunk$set(dev = 'pdf')
```

@@

```{r throughput, fig.cap="Throughput on uniform random workload.\\label{tput}", fig.width=3.5, fig.height=3, echo=F, message=F, warning=F, error=F}
data <- function(d) {
  d$abort_rate <- d$txn_failed / (d$txn_count + d$txn_failed)
  d$throughput <- d$txn_count * num(d$nclients) / d$total_time
  # d$throughput <- d$ntxns * num(d$nclients) / d$total_time
  d$avg_latency_ms <- d$txn_time / d$txn_count * 1000
  return(d)
}

d <- data(db("
  select * from tapir where 
  generator_time is not null and total_time is not null
  and (initusers = 50 or initusers = 500)
  and name like 'claret-v%'
",
  factors=c('nshards', 'nclients'),
  numeric=c('total_time', 'txn_count')
))

ggplot(d, aes(
  x = nclients,
  y = throughput,
  group = ccmode,
  fill = ccmode,
  color = ccmode
))+
# geom_meanbar()+
stat_smooth()+
facet_grid(~nshards, labeller=label_pretty)+
theme_mine
```

>>>>

abstract: |
  Building database applications out of data structures rather than simple string values allows the flexibility and fine-grained control of typical key-value databases while providing better performance and scalability. Composing transactions out of linearizable data structure operations exposes concurrency in a safe way, making it simple to implement efficiently and easy to reason about.
---
```{r setup, include=FALSE}
opts_chunk$set(dev='pdf', echo=F, message=F, warning=F, error=F, fig.width=3.2, fig.height=3)
```

@@

```{r stress, fig.cap="Throughput of SortedSet microbenchmark.\\label{stress_tput}"}
d <- data(db("
    select * from tapir where 
    total_time is not null
    and name like 'stress-v0.14%'
    ", factors=c('nshards', 'nclients'), numeric=c('total_time', 'txn_count')))
d$opmix <- factor(revalue(d$mix, c(
    'mostly_update'='35% read\n65% update',
    'update_heavy'='50% read\n50% update',
    'read_heavy'='90% read\n10% update'
)))
d.u <- subset(d, nshards == 4 & nkeys == 10000 & alpha == 0.6 & grepl('update_heavy|read_heavy', mix))
ggplot(d.u, aes(x=nclients, y=throughput, group=cc, fill=cc, color=cc, linetype=cc))+
    stat_summary(fun.y=mean, geom="line")+
    xlab('Concurrent clients')+ylab('Throughput (transactions / sec)')+
    expand_limits(y=0)+
    facet_wrap(~opmix)+
    theme_mine+theme(legend.position='top', legend.direction='horizontal', legend.title.align=1)+
    cc_scales(title='Concurrency\ncontrol:')
```

```{r throughput, fig.cap="Throughput on social network workloads.\\label{tput}"}
d <- data(db("
    select * from tapir where 
    generator_time is not null and total_time is not null
    and name like 'claret-v0.14%'
  ",
    factors=c('nshards', 'nclients'),
    numeric=c('total_time', 'txn_count')
))
d.u <- subset(d, nshards == 4 & initusers == 4096 & grepl('geom_repost|read_heavy', mix))
ggplot(d.u, aes(x=nclients, y=throughput, group=cc, fill=cc, color=cc, linetype=cc))+
    stat_summary(fun.y=mean, geom="line")+
    xlab('Concurrent clients')+ylab('Throughput (transactions / sec)')+
    expand_limits(y=0)+
    facet_wrap(~workload)+
    theme_mine+theme(legend.position='top', legend.direction='horizontal', legend.title.align=1)+
    cc_scales(title='Concurrency\ncontrol:')
```
